SunPy - Python for Solar Physics

### 2014-01-30 3-2-HEK.tex
HEK section

Simple HEK queries consist of start time, an end time, and an event type 
(Listing~\ref{code:hek:simple}). Event types are specified as upper case, 
two letter strings, and are 
identical to the two letter abbreviations found at the HEK website,
%\href{http://www.lmsal.com/hek/VOEvent_Spec.html}{http://www.lmsal.com/hek/VOEvent_Spec.html}
% schriste - above line causes an error, can't figure out why

@@

The ability to use comparison and logical operators on HEK attributes allows 
the construction of queries of almost arbitrary complexity. 
The results of a HEK query can be used to download the 
corresponding data from the VSO using SunPy's \texttt{H2VClient}.
%schriste - this is a weird way to end this section, either show how it is done or 
% do not mention it, i think.
%dps - I agree.
%JI - I agree
%Stuart: Will do on my next pass
%ays: hmm, still nothing?

>>>>

Simple HEK queries consist of start time, an end time, and an event type 
(Listing~\ref{code:hek:simple}). Event types are specified as upper case, 
two letter strings, and are 
identical to the two letter abbreviations found at the HEK website
(\url{http://www.lmsal.com/hek/VOEvent_Spec.html}).

@@

The ability to use comparison and logical operators on HEK attributes allows 
the construction of queries of almost arbitrary complexity.
%The results of a HEK query can be used to download the 
%corresponding data from the VSO using SunPy's \texttt{H2VClient}.
%schriste - this is a weird way to end this section, either show how it is done or 
% do not mention it, i think.
%dps - I agree.
%JI - I agree
%Stuart: Will do on my next pass
%ays: hmm, still nothing?
% removed sentence until it is fixed.
